---
title: " "
output:
  pdf_document: 
    number_sections: true
geometry: "a4paper, top=1.25in,bottom=1.25in,right=1.25in,left=1.25in"
fontsize: 12pt
header-includes:
  - \usepackage{float}
  - \usepackage{sectsty}
  - \usepackage{paralist}
  - \usepackage{setspace}\spacing{1.5}
  - \usepackage{fancyhdr}
  - \usepackage{lastpage}
  - \usepackage{dcolumn}
  - \usepackage{natbib}\bibliographystyle{agsm}
  - \usepackage[nottoc, numbib]{tocbibind}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

\allsectionsfont{\raggedright}
\subsectionfont{\raggedright}
\subsubsectionfont{\raggedright}

\begin{centering}
\thispagestyle{empty}
\Huge
{\bf P2P Lending Club }

\vspace{0.2cm}
\Large
{Data Analysis}

\vfill
\small
{by}

\vspace{0.2cm}
{Hans Alcahya Tjong (570795) \\ Ananda Eraz Irfananto (547048)}

\vspace{0.5cm}
{Winter semester 21/22}
    
\end{centering}


\newpage
\tableofcontents

\newpage
```{r abstract, child='Abstract_Introduction.Rmd'}
```

\newpage
```{r methodology, child='Methodology.Rmd'}
```

\newpage
```{r empirical, child='Empirical_Results.Rmd'}
```

\newpage
```{r quelle, child='Quelle.Rmd'}
```

\newpage
```{r declaration, child='Declaration.Rmd'}
```
